%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % \begin{cventry}
  % {Robotics, College of Engineering}
  % {Research Assistant}
  % {Ann Arbor, US}
  % {Sept. 2023 - Pre.}
  % {
  %   \begin{cvitems}
  %   \item {Supervised by Prof. Yanran Ding}
  %   \item {Engineered and tested a Dynamometer to serve as the motor-testing platform.}
  %   \item {Developed a control framework facilitating seamless communication between computer, voltmeter, oscilloscope, and torque sensor.}
  %   \item {Established the Electrical experiment platform, setting up equipments such as oscilloscopes, voltmeters, and adjustable DC power supplies.}
  %   \item {Research on the mechanism and control of Brushless DC motor, deploying PID algorithm for high-bandwidth feedback control.}
  % \end{cvitems}
  % }

  % \end{cventry}

  \cventry
  {DEEP Robotics}
  {Motion Control Engineer Intern (MLE)}
  {SJTU, Shanghai, China}
  {May.2023 - Aug.2023}
  {
    \begin{cvitems}
      \item {Migrate "Agile but Safe" to Lite3 robot. Implement a hierarchical DRL model for motion control. \href{https://github.com/priest-yang/ABS-DeepRobotics-Lite3}{\textbf{[Github Repo]}}}
      \item {Reproduce deep tracking control, combining MPC-based and terrain-aware foothold planner with DRL-based motion control. Achieve robust control on extreme risky terrains. Investigate appropriate terrain encoders and reward functions.}
      \item {Modifying PPO algorithm, adding advanced features such as terrain encoder(GRU+LSTM) and symmetric data argumentation.}
    \end{cvitems}
  }



  \begin{cventry}
    {Asset Pro}
    {Quantitative Trading Data Analyst Intern}
    {Shanghai, CN}
    {Feb.2023 - May.2023}
    {
      \begin{cvitems}
        \item {Conducted in-depth research and successfully replicated mainstream fundamental factors.}
        \item {Explored correlation network factors, analyzing stock relationships from various perspectives, achieving an average 20-day increase of 3\% through single-factor analysis.}
        \item {Responsible for researching the data quality of data suppliers, successfully replicating upstream and downstream industry relationship chain factors.}
      \end{cvitems}
    }
    \end{cventry}

  
  % \cventry
  % {ECE2700J Introduction to Logic Design}
  % {Teaching Assistant}
  % {SJTU, Shanghai, China}
  % {May.2023 - Aug.2023}
  % {
  %   \begin{cvitems}
  %     \item {Held regular recitation classes per week in English.}
  %     \item {Held office hours to help students with their homework.}
  %     \item {Held Lab session, debug code for students.}
  %     \item {Grade homework and exams.}
  %   \end{cvitems}
  % }









\end{cventries}






% \end{cventries}



