%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \begin{cventry}
    {Programmer}
    {EV Charging Station Recommendation System}
    {University of Michigan}
    {Sept. 2023 - Dec. 2023}
    {
      \begin{cvitems}
        \item {\textbf{Data scraping} using GoogleMap | Serp | NREL API.}
        \item {\textbf{NLP} comments using ChatGPT API \& \textbf{prompt engineering}.}
        \item {LLM-based embedded vector space \textbf{personalization}.}
        \item {Item-item \textbf{reasoning} based on Collaborative Filtering \& Relevance Matrix.}
        \item {\textbf{“Learn to Rank”} using LightGBM, automatic pesudo-label generation using ChatGPT \& GoogleMap API.}
        \item {Integrated mainstream rankers such as \textbf{BM25}(core feature of Bing), TF-IDF, Pivoted Normalization, DirichletLM.}
        \item {\textbf{MEM-efficient} data structure based on inverted index}
        \item {\textbf{User Interface} based on Flask, GoogleMAP API}
        \item {Project on Github: \href{https://github.com/priest-yang/PlugStation-Recommendation-System}{\textbf{PlugStation-Recommendation-System}}.}
       \end{cvitems}
    }
  \end{cventry}

  \begin{cventry}
    {Embedded System Programmer \& Mechanical Designer}
    {2-Wheel Self Balanced Robot}
    {Shanghai Jiao Tong University}
    {Sept. 2023 - Dec. 2023}
    {
      \begin{cvitems}
        \item {Deploy the \textbf{Linear Quadratic Regulator \& PID} control algorithm for self-balancing.}
        \item {Design \textbf{PCB} for IO expansion and adapt to various peripherals.}
        \item {Realize efficient communication using \textbf{CAN Bus}.}
        \item {Integrate safety alerting using PWM \& Buzzer and Battery monitoring using ADC.}
      \end{cvitems}
    }
  \end{cventry}
  




  % %---------------------------------------------------------
% \cventry
%   {Programmer}
%   {Big data recommendation based on 1 million songs dataset}
%   {Shanghai Jiao Tong University}
%   {May. 2023 - Aug. 2023}
%   {
%     \begin{cvitems}
%       \item {Realize efficient file stream processing and data cleaning (AVRO + Pandas).}
%       \item {Implement BFS-based \& KMeans-based Algorithms to realize diverse recommendation (Python + Spark).}
%       \item {Develop metrics for measuring the similarities between songs.}
%       \item {Project on GitHub: https://github.com/priest-yang/ECE4720J-SU23.}
%      \end{cvitems}
%   } 

  \cventry
    {Team Leader \& Programmer \& Mechanical Designer} % Role
    {Remote Control Mars Rover with Variable Chassis} % Event
    {Shanghai Jiao Tong University} % Location
    {Jul. 2021 ‑ Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Reproduce the classical mechanical chassis structure of \textbf{Curiosity, NASA}.}
        \item {Realize the function of automatic obstacles' avoidance.}
        \item {Realize the function of variable steering strategy.}
        \item {Finite element analysis for critical component.}
        \item {See portfolio page for details: \href{https://priest-yang.github.io/shaoze}{\textbf{Mars' Rover}} }
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
{Structure Designer \& Algorithm Programmer} % Role
{Hex-crab, unmanned seabed landform detector} % Event
{Shanghai Jiao Tong University} % Location
{Nov. 2021 ‑ July. 2022}% Date(s)
{
  \begin{cvitems} % Description(s)
    \item {Realize the structure model of multi-legged bio-robot.}
    \item {Reproduce the gait strategy from another python project.}
  \end{cvitems}
}

% ---------------------------------------------------------

% \cventry
% {Product Promotion Poster} % Role
% {Dégagé White: A brushless tooth flusher} % Event
% {Shanghai} % Location
% {Jun. 2022 ‑ Oct. 2022}% Date(s)
% {
%   \begin{cvitems} % Description(s)
%     \item {Design and realize the promotional video.}
%     \item {Assist the simulation for 3-D model.}
%   \end{cvitems}
% }

% ---------------------------------------------------------


% \cventry
% {Programmer} % Role
% {5-stage pipelined processor based on RISC-V instruction set} % Event
% {Shanghai Jiao Tong University} % Location
% {Sept. 2022 ‑ Dec. 2022}% Date(s)
% {
%   \begin{cvitems} % Description(s)
%     \item {Model and simulate the single cycle processor, 5-stage pipeline processor, the cache through Verilog HDL}
%     \item {Cope with various Hazard types. (Data hazard, EX/MEM hazard, jump hazard)}
%     \item {Implement the virtual memory, the Page Table, the Translation Look-aside Buffer.}
%   \end{cvitems}
% }


\end{cventries}

