%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \begin{cventry}
    {Predicting and Optimizing Workers’ Trust toward Autonomous Vehicles in Manufacturing Plants}
    {The Boeing Company - Industrial \& Operations Engineering}
    {Ann Arbor, US}
    {Sept. 2023 - Pre.}
    {
      \begin{cvitems}
      \item {Co-supervised by Prof. Xi Jessie Yang and Al Salour, Technical Fellow at Boeing}
      \item {Formulate a vertical FSM-based algorithm boosting pedestrian behavior analysis, achieving a 12\% accuracy uplift.
      The paper (first author) \textbf{"Identifying Worker Motion Through a Manufacturing Plant: A Finite Automaton Model"} was accepted by IEEE conference RO-MAN.}
      \item {Based on Temporal Fusion Transformer and VQ-VAE, developing trajectory prediction models. Achieve RMSE < 1m in 4s prediction.}
      \item {Analyze vast experimental data from virtual environment, ensuring real-time communication between Unreal Engine and Python model.}
      \item {Integrate ML model to Unreal Engine, enabling real-time prediction and control of AGV. }
      \item {Develop a Python-based UI (Dash/Plotly) for efficient data-labeling and data flow replay.}
    \end{cvitems}
    }
  
  \end{cventry}

  \begin{cventry}
    {Quadraped Robot Control and Embedding System Development}
    {ARCAD Lab, Robotics Engineering}
    {Ann Arbor, US}
    {Oct. 2023 - Pre.}
    {
      \begin{cvitems}
        \item {Supervised by Prof. Yanran Ding}
        \item {On the Anymal robot, deploying teacher-student architecture to accelerate the training process of reinforcement learning model}
        % \item {Read multiple physical parameters from Isaac gym, including the  contact conditions, friction coefficient, contact forces, elevation map.}
        \item {Under development: (Sim2Real) based on Unitree Go2 model, communicate with robot PC through Ethernet port and Unitree SDK}
        \item {Engineered and tested a Dynamometer to serve as the motor-testing platform. Developed a control framework facilitating seamless communication between computer, voltmeter, oscilloscope, and torque sensor.}
        \item {Research on the mechanism and control of Brushless DC motor, deploying PID algorithm for high-bandwidth feedback control.}
      \end{cvitems}
    }
  
  \end{cventry}

  \begin{cventry}
    {Style Analysis of Chinese Landscape Painting Based on Artificial Intelligence} % Job title
    {SJTU AI Institute} % Organization
    {Shanghai Jiao Tong University} % Location
    {Dec. 2021 - Jul. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Developed a novel hierarchical model for the restoration of Chinese landscape paintings, effectively preserving fine-grained brushstrokes and artistic styles.
      Co-first author of paper titled \href{https://link.springer.com/content/pdf/10.1007/s44267-023-00021-y.pdf}{\textbf{"Hierarchical Painter: Chinese Landscape Painting Restoration with Fine-grained Styles"}} was published at journal Visual Intelligence.
      \item Led the design and experimentation of a segmentation-based detail generation model, enhancing the consistency and authenticity.
      % \item Research on new-style edge detection and texture generation.
      % \item {See portfolio page for details: \href{https://priest-yang.github.io/shaoze}{\textbf{Hierarchical Painter}} }
      \end{cvitems}
    }
  \end{cventry}
    

    
\end{cventries}

